---
title: "Test Miami-Dade SIR Report"
author: "Anshul Saxena and Gabriel Odom"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**THIS IS A TEST OF THE REPORTING AND PUBLISHING CAPABILITIES OF THE `reticulate` PACKAGE LINKING PYTHON TO RMARKDOWN. THIS REPORT IS NOT INTENDED TO PROVIDE ANY INSIGHT INTO THE CURRENT COVID-19 PANDEMIC IN MIAMI-DADE COUNTY. INSPECT AT YOUR OWN RISK.**

## Setup
We need to load some R packages before we can perform our computing.
```{r, message=FALSE}
library(reticulate)
library(tidyverse)
```

The shell script to install the packages we need is in `src/install_python_packages_20200403.sh`. This creates a conda environment called `env_sflCHIME` and activates it. At current, I have been unable to run these commands on Windows.

<!-- There is another way: using the Anaconda Navigator GUI, -->

<!-- 1. Click "Environments" (top left under "Home") -->
<!-- 2. Click "Create" (the plus sign) -->
<!-- 3. In the pop-up, give the environment a name, select a Python version (I chose 3.6), and select if you wany to include R or not. -->
<!-- 4. In the "Search Packages" box, type the packages that you need (`altair`, `pandas`, and `numpy`). -->

On Mac, I have a Conda environment created for this project. In the terminal, I type `which python` and it tells me
```{bash, eval=FALSE}
which python
```
```
/Users/gabrielodom/anaconda3/envs/env_sflCHIME/bin/python
```

If it says
```
/usr/bin/python
```
(or some other place), then something is wrong.

I specifically want this python environment, so I "point" `reticulate` to the particular environment that we installed with Anaconda, replete with the version of Python we selected and all associated libraries. (**NOTE**: this line must be executed before any other `reticulate` functions or Python calls, otherwise it will have no effect.)
```{r}
use_python(
    "/Users/gabrielodom/anaconda3/envs/env_sflCHIME/bin/python",
    required = TRUE
)
```

We also have some Python libraries to load.
```{python}
from functools import reduce
from typing import Tuple, Dict, Any
import pandas as pd
import streamlit as st
import numpy as np
import altair as alt
```

IT WORKS!!!!!! (This seriously took a full weekend to figure out, and then I called in the big guns: Tim N. and Athina H. Note that this is not compatible with environments created via Anaconda, at least not by default.)

*******************************************************************************
</br>

## Parameters
Now, we want to set our initial parameters. We organise them the same way as on the CHARM app.

### Hospital Parameters
```{python}
# Regional Population
S_default = 2761581.0

# Hospital Market Share
Penn_market_share = 0.15

# Currently Hospitalised Patients (at current hospital?)
known_cases = 400.0
current_hosp = known_cases

# Currently Hospitalised Patients
known_infections = 1000.0
initial_infections = known_infections
```

### Spread and Contact Parameters
```{python}
# Doubling Time
doubling_time = 6.0

# Social Distancing (% reduction in social contact)
relative_contact_rate = 0.0
```

### Severity Rates
```{python}
# Hospitalisation (% of total infections)
hosp_rate = 0.05

# ICU (% of total infections)
icu_rate = 0.02

# Ventilated (% of total infections)
vent_rate = 0.01
```

### Severity Times
```{python}
# Infectious Days
recovery_days = 14.0

# Average hospital length of stay (days)
hosp_los = 7.0

# Average ICU length of stay (days)
icu_los = 9.0

# Average length of stay on a ventilator (days)
vent_los = 10.0
```


## Directly Estimated Parameters
Given the parameters above, we calculate the following disease spread parameters.

### SIR Initial Values
```{python}
total_infections = current_hosp / Penn_market_share / hosp_rate
print(total_infections)

detection_prob = initial_infections / total_infections
print(detection_prob)

Infct = initial_infections / detection_prob
Susc, Infct, Recov = S_default - Infct, Infct, 0.0
print(Susc)
print(Infct)
# print(Recov)
# type(Recov)

intrinsic_growth_rate = 2 ** (1 / doubling_time) - 1
print(intrinsic_growth_rate)
```
**NOTE**: the total infections and initial infections are equal at $t = 0$.

### SIR Transition Rates
```{python}
# type(Recov)
# print(Recov)

gamma = 1.0 / recovery_days
# mean recovery rate, gamma, (in 1/days).
print(gamma)

beta = (intrinsic_growth_rate + gamma) / Susc * (1.0 - relative_contact_rate)
# Contact rate, beta
# {rate based on doubling time} / {initial Susc}
print(beta)

r_t = beta / gamma * Susc 
# Current Reproduction Number
# r_t is r_0 after distancing
print(r_t)

r_naught = r_t / (1.0 - relative_contact_rate)
# Initial Reproduction Number
print(r_naught)

doubling_time_t = 1.0 / np.log2(beta * Susc - gamma + 1.0) 
# Current Doubling Time
# doubling time after distancing
print(doubling_time_t)

# type(Recov)
```

As an aside, if I want to access any of these values in R (for instance, $R_0$), I can call them as `py$r_naught`, which yields `r py$r_naught`.

*******************************************************************************
</br>

## Model Specification
We can now specify the SIR model at outset and over time.
```{python}
# type(Recov)

# SIR at Outset
def sir(y, beta, gamma, N):
    S, I, R = y
    Sn = (-beta * S * I) + S
    In = (beta * S * I - gamma * I) + I
    Rn = gamma * I + R
    if Sn < 0:
        Sn = 0.0
    if In < 0:
        In = 0.0
    if Rn < 0:
        Rn = 0.0

    scale = N / (Sn + In + Rn)
    return Sn * scale, In * scale, Rn * scale
    
# type(Recov)

# Dynamic SIR 
def sim_sir(S, I, R, beta, gamma, n_days, beta_decay = None):
    N = S + I + R
    s, i, r = [S], [I], [R]
    for day in range(n_days):
        y = S, I, R
        S, I, R = sir(y, beta, gamma, N)
        if beta_decay:
            beta = beta * (1 - beta_decay)
        s.append(S)
        i.append(I)
        r.append(R)
            
    s, i, r = np.array(s), np.array(i), np.array(r)
    return s, i, r

# type(Recov)

# Test Function
def test_fun(x):
  y = x + 2
  return y
  
# type(Recov)
```

Run the model, assuming no decay in contact rate over the next 30 days.
```{python}
n_days = 100
beta_decay = 0.0

test_fun(3)
# type(Susc)
# type(Infct)
# type(Recov)
y = Susc, Infct, Recov
# print(y)
# type(y)
N = Susc + Infct + Recov
print(N)
type(N)
sir(y, beta, gamma, N)
s, i, r = sim_sir(
  Susc, Infct, Recov, beta, gamma, n_days, beta_decay = beta_decay
)
```
**ERROR**: `Error in py_call_impl(callable, dots$args, dots$keywords) : `
`  TypeError: unsupported operand type(s) for +: 'float' and 'type'`  
**SOLUTION**: I can't have a Python object named `R`.

We now inspect the results of this model
```{r}
res_df <- tibble(
    days  = seq_len(py$n_days + 1),
    Susc  = py$s,
    Infct = py$i,
    Recov = py$r
)

ggplot(data = res_df) +
    aes(x = days) +
    geom_line(aes(y = Susc), colour = "black") + 
    geom_line(aes(y = Infct), colour = "red") + 
    geom_line(aes(y = Recov), colour = "green")
```

